MSDS 6372 Project 1 Objective 1

### 2020-02-06 Codebook/MSDS6372.Project.O1.Rmd

```{r data prep}
nycraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
head(nycraw)
str(nycraw)
```

@@

```{r linearity check w/ Price > 400 Outliers Removed}
nyc.cat.model<-lm(price~.,data=nyc.categorical) 
#nyc4 %>% pairs() No color model
pairs(nyc.categorical,col=nyc.categorical$neighbourhood_group) #Color by neighborhood

@@

```{r linearity check w/ Log-Linear model Price > 400 Outliers Removed}
log.nyc.outliers <- log.nyc[!(log.nyc$lprice > 400),]

@@

- Independence
  - Assumed
- Multicollinearity
  - Confirmed with VIFs and pairs plot that there is no mjultcollinearity occuring
```{r multicollinearity assumption 2}
vif(log.depend.model)[,3]^2
```

- Removed all prices over 400 to help reduce data set and uncover any correlation that was present between the dependent varaibles and independent categorical variables
```{r outliers assumption}
#log.nyc.outliers <- log.nyc[!(log.nyc$lprice > 400),]
```

@@

```{r full model check for linearity}
nyc.model = lm(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers)
summary(nyc.model)
```

@@

#### KNN or Random Forest
- Multiple linear regression is just one option in building a predictive model for a continuous response
- We are seeing it as a bad option because
  - The true relationship between the response and predictors is NOT “linear”.  The relationships are complex.
    - We have gotten close, but we have worked extremely hard in specifying our model and manipulate the raw data to surface a linear relationship
    - This makes the interpretation into the real world difficult to translate and understand
  - Since the above is true and our data is very large, we think that other methods such as Random Forest or K-NN would perform better.
    - These options are less time consuming because the model complexity is built into the lagorithm
    - We also do not have to specify how a relationship exists ahead of time
- Since we see a strong relationship between the categorical variables and we have not yet learned Random Forest models, we move forward with a Two-Way ANOVA model to create a sound model to predict the price of a NYC AirBnB.

>>>>

```{r data prep}
nycraw <- read.csv("https://raw.githubusercontent.com/JaclynCoate/6372_Project_1/master/AB_NYC_2019.csv", header = TRUE, strip.white=TRUE)
head(nycraw)
str(nycraw)
```

@@

```{r linearity check w Price greater than 400 Outliers Removed}
nyc.cat.model<-lm(price~.,data=nyc.categorical) 
#nyc4 %>% pairs() No color model
pairs(nyc.categorical,col=nyc.categorical$neighbourhood_group) #Color by neighborhood

@@

```{r linearity check w Log-Linear model Price greater than 400 Outliers Removed}
log.nyc.outliers <- log.nyc[!(log.nyc$lprice > 400),]

@@

@@

```{r full model check for p-value significance}
nyc.model = lm(lprice~neighbourhood_group + room_type + neighbourhood_group:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count, data=log.nyc.outliers)
summary(nyc.model)
```

@@

- Independence
  - Assumed
- Multicollinearity
  - Confirmed with VIFs and pairs plot that there is no mjultcollinearity occuring

```{r multicollinearity assumption two}
vif(log.depend.model)[,3]^2
```

- Removed all prices over 400 to help reduce data set and uncover any correlation that was present between the dependent varaibles and independent categorical variables

```{r outliers assumption}
#log.nyc.outliers <- log.nyc[!(log.nyc$lprice > 400),]
```

#### MLR May Not Be The Best
- Multiple linear regression is just one option in building a predictive model for a continuous response
- We are seeing it as a bad option because
  - The true relationship between the response and predictors is NOT “linear”.  The relationships are complex.
    - We have gotten close, but we have worked extremely hard in specifying our model and manipulating the raw data to surface a linear relationship
    - This makes the interpretation into the real world application difficult to interpret
  - Since the above is true and our data is very large, we think that other methods such as Random Forest or K-NN would perform better.
    - These options are less time consuming because the model complexity is built into the lagorithm
    - We also do not have to specify how a relationship exists ahead of time
- Since we see a strong relationship between the categorical variables, we move forward with a Two-Way ANOVA model to create a model way predict the price of a NYC AirBnB.
